Abstraction and Invariance for Algebraically Indexed Types

### 2012-10-23 paper/paper.tex
Final small changes
New framework setup
More cleanup
acknowledgements, popl copyright etc

\documentclass[preprint]{sigplanconf}

@@

\newcommand{\relEnv}[1]{\mathcal{#1}}
\newcommand{\tySem}[1]{\llbracket #1 \rrbracket^{\mathcal{T}}}
\newcommand{\ctxtSem}[1]{\llbracket #1 \rrbracket^{\mathcal{C}}}
\newcommand{\tmSem}[1]{\llbracket #1 \rrbracket^{\mathit{tm}}}
\newcommand{\tyPrimSem}[1]{\llbracket #1 \rrbracket^{\mathcal{T}_0}}
\newcommand{\rsem}[3]{\llbracket #1 \rrbracket^{\mathcal{R}}_{#2}{#3}}
\newcommand{\extends}[2]{\mathsf{ext}(#1,#2)}

@@

\newtheoremstyle{examplestyle}
  {\topsep}  % space above
  {\topsep}  % space below
  {\normalfont}% name of font to use in the body of the theorem
  {0em}% measure of space to indent
  {\bfseries}% name of head font
  {.}% punctuation between head and body
  {5pt plus 1pt minus 1pt}% space after theorem head; " " = normal interword space
  {}% Manually specify head
\theoremstyle{examplestyle}
\newtheorem{example}{Example}

@@

@@

@@

\bibitem{bernardy12proofs} 
J.-P.~Bernardy, P.~Jansson, R.~Paterson.
Proofs for free: Parametricity for dependent types.
{\em Journal of Functional Programming} 22(2), pp. 107-152, 2012.

@@

\bibitem{hofmann08correctness}
M.~Hofmann. Correctness of effect-based program
transformations. Formal Logical Methods for System Security and
Correctness, pp. 149-173, 2008.

>>>>

\documentclass{sigplanconf}

@@

\newcommand{\relEnv}[1]{\mathcal{#1}}
%\newcommand{\tySem}[1]{\llbracket #1 \rrbracket^{\mathcal{T}}}
%\newcommand{\ctxtSem}[1]{\llbracket #1 \rrbracket^{\mathcal{C}}}
%\newcommand{\tmSem}[1]{\llbracket #1 \rrbracket^{\mathit{tm}}}
%\newcommand{\tyPrimSem}[1]{\llbracket #1 \rrbracket^{\mathcal{T}_0}}
\newcommand{\tySem}[1]{\left| #1\right|}
\newcommand{\ctxtSem}[1]{\left| #1\right|}
\newcommand{\tmSem}[1]{\left| #1\right|}
\newcommand{\tyPrimSem}[1]{\left| #1\right|}
\newcommand{\rsem}[1]{\llbracket #1 \rrbracket}
\newcommand{\extends}[2]{\mathsf{ext}(#1,#2)}

@@

\newtheoremstyle{examplestyle}
  {\topsep}  % space above
  {\topsep}  % space below
  {\normalfont}% name of font to use in the body of the theorem
  {0em}% measure of space to indent
  {\bfseries}% name of head font
  {.}% punctuation between head and body
  {5pt plus 1pt minus 1pt}% space after theorem head; " " = normal interword space
  {}% Manually specify head
\theoremstyle{examplestyle}
\newtheorem{example}{Example}
\newtheorem*{example*}{Example}

@@

\conferenceinfo{POPL'13,} {January 23--25, 2013, Rome, Italy.}
\CopyrightYear{2013}
\copyrightdata{978-1-4503-1832-7/13/01}

@@

\section*{Acknowledgements}
The authors would like to thank Nick Benton, John Reppy and Martin Will for 
illuminating discussions on geometry and types.

@@

\bibitem{bernardy12proofs} 
J.-P.~Bernardy, P.~Jansson, R.~Paterson.
Proofs for Free: Parametricity for Dependent Types.
{\em Journal of Functional Programming} 22(2), pp. 107-152, 2012.

@@

\bibitem{hofmann08correctness}
M.~Hofmann. Correctness of Effect-based Program
Transformations. Formal Logical Methods for System Security and
Correctness, pp. 149-173, 2008.
